---
title: "Weight of Fish"
author: "Hannah Vong"
date: "`(10/31/2023)`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight

find the best model using 2 variables to predict Perch weight, and compare this to the best over-all model.


## Perch

```{r}
perch = filter(fish, Species == 'Perch')
```

### Best Two regressor model


```{r}
modelPerch = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = perch)
summary(modelPerch)

```


```{r}
bestPerch = lm(Weight ~ Height + Width, data = perch)
summary (bestPerch)
```
### best 2 - variable equation
Weight = -536 + 77.77*Height + 69.62*Width


## Pike

```{r}
pike = filter(fish, Species == 'Pike')
```





### Best Two regressor model


```{r}
modelPike = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = pike)
summary(modelPike)

```
```{r}
bestPike = lm(Weight ~ Height + Width, data = pike)
summary (bestPike)
```
### best 2 - variable equation
Weight = -142397 + 214.82*Height + 95.47*Width

## Roach

```{r}
roach = filter(fish, Species == 'Roach')
```

### Best Two regressor model

```{r}
modelRoach = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = roach)
summary(modelRoach)

```

```{r}
bestRoach = lm(Weight ~ Height + Width, data = roach)
summary (bestRoach)
```
### best 2 - variable equation
Weight = -286.164+ 9.467*Height + 102.473*Width


## Final Summary Statements
The best  model using two variables to predict Perch is Weight = -536 + 77.77*Height + 69.62*Width, The best  model using two variables to predict Pike is Weight = -142397 + 214.82*Height + 95.47*Width. The best  model using two variables to predict Roach is Weight = -286.164+ 9.467*Height + 102.473*Width.

